---
title: "Naming Columns with Function Arguments"
author: "Connor Krenzer"
date: "4/17/2021"
output: html_document
---

This was written under R version 4.0.5.

```{r setup, echo = FALSE}

#If you do not know what this does, do not worry.
#You can kindly ignore this chunk of code.
knitr::opts_chunk$set(echo = TRUE,
                      include = TRUE,
                      results = "hide",
                      error = TRUE,
                      warning = TRUE,
                      message = TRUE,
                      eval = TRUE)

```



First things first. Let's load in dplyr. 

```{r packages, message = FALSE}

if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr)

```







Writing functions is key to being a successful R programmer. If you wanted to create a new column using a mutate() call, it would be of this form:

```{r example, eval = FALSE}

df %>% 
  mutate(NEW_VARIABLE = "VALUES OF NEW VARIABLE")

```

The variable name is on the left-hand side of the expression and the values of the new column are on the right-hand side. That's pretty straightforward. But what happens when you try to do the same thing within a function call?

Before that, let's remind ourselves of what happens when you create a new variable using the built-in `women` dataset:

```{r new variable, results = "show"}

women %>% 
  mutate(bmi = (weight / (height^2)) * 703)


```


Great! We created a new variable called `bmi` with that mutate() call. Now, back to our question: "What happens when you try to create a new variable using the argument of a function as the new column's name?"

There is only one way to find out. Let's make a function that calculates BMI and test it out:

```{r bmi calculator, results = "show"}

bmi_calculator <- function(df, NEW_VARIABLE_NAME){
     df %>%
          mutate(NEW_VARIABLE_NAME = (weight / (height^2)) * 703)
}

```

Let's see just the first six observations:

```{r bmi_calculator test, results = "show"}

bmi_calculator(df = women, NEW_VARIABLE_NAME = "bmi") %>% 
  head()

```


Rather than creating a new column called __bmi__, bmi_calculator() created a new column with the name of the parameter instead of the value of the parameter! mutate() assumed we wanted the name of the column to be NEW_VARIABLE_NAME instead of the value of the parameter that has the same name.

How do we fix this? How do we get the new column to say "bmi"? We have to add double curly-braces and use the unpacking `:=` operator. Compare the first function to the one below:


```{r working version}

 bmi_calculator_that_works <- function(df, NEW_VARIABLE_NAME){
     df %>%
          mutate({{NEW_VARIABLE_NAME}} := (weight / (height^2)) * 703)
}

```

The function now works as desired:

```{r desired output, results = "show"}

bmi_calculator_that_works(df = women, NEW_VARIABLE_NAME = "bmi") %>% 
  head()

```


What do these changes do? The `:=` from {rlang} processes the left side before mutate() assigns a variable name, so the passed in variable-- **NEW_VARIABLE_NAME**--can get unpacked into the user's input--"bmi", in this case. In other words, `:=` recognizes that __{{NEW_VARIABLE_NAME}}__ contains a value, and that the user wants the value contained within __{{NEW_VARIABLE_NAME}}__ to be used as the name of the column.


